% !TEX program = xelatex
\documentclass{article}
\usepackage[margin=0.54in]{geometry}
\usepackage{amsmath, graphicx}
\usepackage{times}

% Link Colors
\usepackage{xcolor}
\definecolor{my_colour}{HTML}{000000}
\definecolor{myblue}{HTML}{2358C4}

\usepackage{hyperref}
\hypersetup{colorlinks, citecolor=myblue, filecolor=myblue, linkcolor=myblue, urlcolor=myblue}

\usepackage{sectsty}
\sectionfont{\large}

% section spacing
\usepackage{titlesec}
\titlespacing\section{0pt}{16pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\usepackage{enumitem}
\setlength{\parindent}{0cm}
\setlist{nolistsep}



\begin{document}
\thispagestyle{plain}
% =================================== HEADER ===================================
\begin{center}
\LARGE \textbf{\textcolor{my_colour}{Edward (Eddie) Guo}} \vspace{.2em}

\normalfont \normalsize
(587) 988-0292
    \hspace{.15em} $\diamond$ \hspace{.15em}
\href{mailto:edward.guo1@ucalgary.ca}{\textcolor{black}{edward.guo1@ucalgary.ca}}
    \hspace{.15em} $\diamond$ \hspace{.15em}
\href{https://www.linkedin.com/in/eguo1}{\textcolor{black}{linkedin.com/in/eguo1}}
    \hspace{.15em} $\diamond$ \hspace{.15em}
\href{https://tig3r66.github.io/index.html}{\textcolor{black}{tig3r66.github.io}}
\end{center}

\vspace{-1em}


% ================================== EDUCATION ================================== 
\section*{\textcolor{my_colour}{Education}}
\vspace{-.25em} \hrulefill \vspace{.25em}

\textbf{University of Calgary} \hfill Jul. 2022 -- Apr. 2025 \\
\textit{Doctor of Medicine (MD)}
\begin{itemize}
    \item President of the Class of 2025
    \item Awarded \$2,500 for academic achievements
\end{itemize} \vspace{1em}

\textbf{University of Alberta} \hfill Sep. 2020 -- Apr. 2022 \\
\textit{Bachelor of Science, Engineering Physics (Partially completed degree)} \hfill GPA: 4.00/4.00
\begin{itemize}
    \item Awarded \$27,000+ for leadership and academic achievements
    \item Awarded \$17,500+ for nerve regeneration and exoskeleton control systems research
    \item Top of class in English critical analysis, multivariable calculus, and organic chemistry II; SAT Math Level 2: 800/800
\end{itemize} \vspace{1em}

\textbf{New College, University of Oxford} \hfill May 2021 -- Aug. 2021 \\
\textit{Study Abroad, Magnetic Resonance Imaging and Stem Cell Engineering} \hfill First Class Honours \\

\textbf{University of Alberta} \hfill Sep. 2018 -- Apr. 2020 \\
\textit{Bachelor of Science Honours, Neuroscience (Partially completed degree)} \hfill GPA: 4.00/4.00


% ================================== RESEARCH ==================================
\section*{\textcolor{my_colour}{Research Experience}}
\vspace{-.25em} \hrulefill \vspace{.25em}

\textbf{Project neuroArm} \hfill Jul. 2022 -- Present\\
\textit{Research Trainee (PI: Dr. Garnette Sutherland, Div. of Neurosurgery)}
\begin{itemize}
    \item Designing machine learning-driven platforms for surgical devices and education; projects include automatic surgeon identification using their surgical tool force profile, quantification of force components which differentiate `expert' vs `novice' surgeons, and an end-to-end platform to track surgical trainee progress
    \item Ideating and analyzing clinical trials to assess the efficacy of the SmartForceps system for surgical education
\end{itemize} \vspace{1em}

\textbf{Collavidence} \hfill Jul. 2022 -- Present\\
\textit{Consultant (PI: Dr. Mayank Goyal, Div. of Neuroradiology)}
\begin{itemize}
    \item Investigating stroke clinical trials (e.g., ESCAPE-NA1); analyzing neuroimaging methods to recommend new standards of care
    \item Using computer vision and deep learning to automate semantic segmentation of brain lesions due to stroke
    \item Developing value propositions to aid clients globally for scientific fundraising in stroke research
\end{itemize} \vspace{1em}

\textbf{Telerobotic and Biorobotic Systems Group} \hfill Sep. 2021 -- Present\\
\textit{Research Assistant (PI: Dr. Mahdi Tavakoli, Dept. of Electrical and Computer Engineering)}
\begin{itemize}
    \item Leading the development of a voice-controlled exoskeleton; users complete tasks 54\% faster than using a mobile app; media coverage: \href{https://edmonton.ctvnews.ca/u-of-a-integrating-artificial-intelligence-into-exoskeleton-technology-1.6019787}{CTV interview} and \href{https://www.linkedin.com/posts/university-of-alberta_ai-voice-controlled-exoskeleton-activity-6954902847477997568-CTf4?utm_source=linkedin_share&utm_medium=member_desktop_web}{University of Alberta interview}
    \item Designing reinforcement learning algorithms for exoskeletons to personalize the patient rehabilitation process; implemented the state-of-the-art TD3 algorithm on a lower-limb exoskeleton to intelligently detect and set a user's desired walking speed
\end{itemize} \vspace{1em}

\textbf{Zochodne Laboratory, University of Alberta} \hfill Oct. 2018 -- Oct. 2020 \\
\textit{Research Assistant (PI: Dr. Douglas Zochodne, Div. of Neurology)}
\begin{itemize}
    \item Studied mouse models of peripheral nerve damage to improve patient outcomes after injury
    \item Performed mouse sciatic nerve microsurgery, electroporation, immunohistochemistry, co-IP, and Western blot
\end{itemize}


% ================================== ACADEMIC PUBLICATIONS ==================================
\section*{\textcolor{my_colour}{Academic Publications, Conferences, Abstracts}}
\vspace{-.25em} \hrulefill \vspace{.25em}

\begin{enumerate}[itemsep=1em]
    % \item \textbf{E. Guo}, A. Baghdadi, R. Singh, S. Lama, G. Sutherland, ``What Makes a Surgeon Unique? Machine Learning for Surgeon Identification Using Their Force Profile,'' \textit{Journal of Neurosurgery: 2023 AANS Annual Scientific Meeting} [in review].
    % \item \textbf{E. Guo}, A. Baghdadi, R. Singh, S. Lama, G. Sutherland, ``Machine Learning Characterization of Important Tool-Tissue Interaction Forces Using Bipolar Forceps,'' \textit{Journal of Neurosurgery: 2023 AANS Annual Scientific Meeting} [in review].
    % \item J. K. Mehr, \textbf{E. Guo}, M. Akbari, V. K. Mushahwar, M. Tavakoli, ``Deep Reinforcement Learning Based Personalized Locomotion Planning for Lower-Limb Exoskeletons,'' \textit{IEEE International Conference on Robotics and Automation} [in review].
    % \item \textbf{E. Guo}, C. Perlette, M. Sharifi, L. Grasse, M. Tata, V. K. Mushahwar, M. Tavakoli, ``Speech-Based Human-Exoskeleton Interaction for Lower Limb Motion Planning,'' \textit{Mechatronics} [in review].
    \item S. Becker, D. Clark, M. Gupta, S. Kannappan, B. Wong, E. Hernandez-Zavaleta, and \textbf{E. Guo}, ``More than a Eureka Moment: Undergraduate Students' Reflective Understanding of Science Inquiry in a Citizen Science Project,'' \textit{Alberta Science Education Journal}, vol. 48, no. 1, pp. 22-36, Jun. 2022.
    \item \textbf{E. Guo}, P. Torabi, D. E. Nielsen, and M. Pietrosanu, ``Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity,'' \textit{STEM Fellowship Journal}, Jan. 2022, doi: 10.17975/sfj-2021-013.
    \item S. Becker, D. Clark, M. Gupta, S. Kannappan, B. Wong, \textbf{E. Guo}, and E. Hernandez-Zavaleta, ``Deepening Undergraduate Student Understanding of Science Inquiry by Reflecting on the Creation and Enactment of a Citizen Science Project,'' presented at the Canadian Society for the Study of Education XLIX Annual Conference, Canada, May 30--June 3, 2021.
\end{enumerate}

% ================================== NON-ACADEMIC PUBLICATIONS ==================================
\section*{\textcolor{my_colour}{Non-Academic Publications}}
\vspace{-.25em} \hrulefill \vspace{.25em}

\textbf{A Gentle Introduction to Data Science with R} \hfill Dec. 2020 -- May 2022
\begin{itemize}
    \item Authored an \href{https://youreka-textbook.netlify.app/}{interactive e-textbook on R programming and data science} used by 600+ students across Canada
\end{itemize} \vspace{1em}

\textbf{Atom Magazine for Engineering Physics} \hfill Dec. 2021 -- Feb. 2022
\begin{itemize}
    \item Founded and wrote the \href{https://atom-winter-2022.netlify.app/}{Atom Magazine for Engineering Physics}; the first issue attracted 300+ readers in 6 countries
\end{itemize}


% ================================== EMPLOYMENT ================================== 
\section*{\textcolor{my_colour}{Employment}}
\vspace{-.25em} \hrulefill \vspace{.25em}

\textbf{University of Alberta} \hfill Sep. 2020 -- Apr. 2022 \\
\textit{Teaching Assistant, Introduction to Tangible Computing I \& II}
\begin{itemize}
    \item Supported a class of 160+ students to understand algorithms and data structures in Python and C++
    \item Received an overall effectiveness rating of 93\% from anonymized student feedback surveys
    \item Collaborated with a team of 16 teaching assistants to facilitate course delivery
\end{itemize} \vspace{1em}

\textbf{Edmonton Fencing Club} \hfill Nov. 2016 -- Oct. 2020 \\
\textit{Fencing Coach}
\begin{itemize}
    \item Coached classes of 5-25 children and teenagers and engaged their parents about their child's progress
    \item Gave private lessons, taught strategic fencing thinking, and resolved student conflicts
\end{itemize}


% ================================== RESEARCH GRANTS ================================== 
\section*{\textcolor{my_colour}{Research Grants}}
\vspace{-.25em} \hrulefill \vspace{.25em}

\textbf{NSERC Undergraduate Student Researcher Award (\$8,500)} \hfill Mar. 2022
\begin{itemize}
    \item Awarded for project titled ``Intelligent control of a lower-limb exoskeleton''
\end{itemize} \vspace{1em}

\textbf{Dean's Research Award (\$500)} \hfill Sep. 2021
\begin{itemize}
    \item Awarded for project titled ``Speech-based locomotion planning for lower-limb exoskeletons''
\end{itemize} \vspace{1em}

\textbf{Alberta Innovates Summer Research Studentship (\$6,000)} \hfill Apr. 2020
\begin{itemize}
    \item Awarded for project titled ``Skin and Nerves: Understanding the dialogue between axons and skin cells to restore sensation''
\end{itemize} \vspace{1em}

\textbf{Office of the Provost and VP (Academic) Summer Studentship Award (\$2,600)} \hfill May 2019
\begin{itemize}
    \item Awarded for project titled ``Axon regrowth and plasticity in diabetic neuropathy: the role of growth cone molecules''
\end{itemize}


% ================================== SPORTS AWARDS ================================== 
\section*{\textcolor{my_colour}{Selected Sports Awards} \normalfont{(of 18 International and National Awards)}}
\vspace{-.25em} \hrulefill \vspace{.25em}

\textbf{Fencing (Foil)} \hfill Feb. 2011 -- Oct. 2020
\begin{itemize}
    \item Accepted annually as a High Performance Program Athlete with the Canadian Fencing Federation \hfill Jan. 2013 -- Dec. 2018
    \item Medalled in 5 Canadian national competitions in the open, U20, U17, and U13 categories \hfill Jan. 2013 -- Dec. 2018
    \item Achieved USA Fencing A16 ranking (highest ranking in USA Fencing) \hfill Dec. 2016
    \item 23rd Place Guatemala Junior (U20) World Cup; represented Team Canada \hfill Dec. 2016
\end{itemize}


% ================================== HONOURS AND AWARDS ================================== 
\section*{\textcolor{my_colour}{Selected Scholarships and Awards} \normalfont{(of 21)}}
\vspace{-.25em} \hrulefill \vspace{.25em}

\textbf{Peter Lougheed Scholarship (\$10,000)} \hfill Sep. 2021
\begin{itemize}
    \item Awarded to University of Alberta students who demonstrate leadership through involvement in university or community organizations, sports activities, or cultural activities and academic achievement
\end{itemize} \vspace{1em}

\textbf{Louise McKinney Post-Secondary Scholarship (\$2,500 x3)} \hfill Dec. 2019, Sep. 2020, Nov. 2022
\begin{itemize}
    \item Awarded on the basis of superior academic achievement (top 1.5-2\% of faculty) to students at the University of Alberta and Calgary who are also Alberta residents; awarded for the 2018/19, 2019/20, and 2021/22 academic terms
\end{itemize} \vspace{1em}

\textbf{Undergraduate Big Data Challenge Research Excellence Award (\$500)} \hfill Jul. 2020
\begin{itemize}
    \item Used unsupervised learning, feature selection, and neural networks to predict cancer response to chemotherapies
\end{itemize} \vspace{1em}

\textbf{Alberta Innovates COVID-19 Hackathon Post-Secondary Student Award (\$500)} \hfill May 2020
\begin{itemize}
    \item Created an interactive app to model how COVID-19 spreads given age, poverty, income, and population density
    \item Media coverage: \href{https://www.folio.ca/students-develop-online-tool-to-predict-covid-19-spread-based-on-demographics/}{University of Alberta Folio article} and the \href{https://genomealberta.ca/genomics/genomics_blog_08182001.aspx}{Genome Alberta podcast}
\end{itemize}


% ================================ EXTRACURRICULAR ACTIVITIES ================================
\section*{\textcolor{my_colour}{Leadership and Volunteer Experience}}
\vspace{-.25em} \hrulefill \vspace{.25em}

\textbf{Calgary Medical Students' Association} \hfill Sep. 2022 -- Present \\
\textit{President}
\begin{itemize}
    \item Chairing the Committee on Accreditation of Canadian Medical Schools (CACMS) Independent Student Analysis Committee for evaluation of the MD Program at the Cumming School of Medicine
    \item Created a support and resource platform for students to share and access study materials; created multiple videos on course concepts, developed tools for career exploration, exams, shadowing, research, shared course notes
    \item Collaborated with Undergraduate Medical Education to arrange 6 small group and exam review sessions for students
    \item Provided  governance, representation, and communication for all matters pertaining to the general welfare and activities of 400+ MD students at the Cumming School of Medicine
\end{itemize} \vspace{1em}

\textbf{Youreka Canada} \hfill Feb. 2019 -- Present \\
\textit{Consultant, National Strategy Team (Jun. 2022 -- Present)}
\begin{itemize}
    \item Collaborating on national equity, diversity, and inclusion policies affecting 200+ students across Canada
    \item Developing national and international expansion plans for regional Youreka branches
\end{itemize} \vspace{1em}
\textit{Vice President, Department of Programs (May 2020 -- Jun. 2022)}
\begin{itemize}
    \item Led a team of 17 PhD, MD, and BSc students to create and deliver the Youreka national curriculum; generated 15,000+ hours of research education for 200+ high school and undergraduate students annually across Canada
    \item Published an academic paper highlighting student development in Youreka in the Alberta Science Education Journal (2022)
\end{itemize} \vspace{1em}
\textit{National Operations Committee Member (May 2020 -- Jun. 2022)}
\begin{itemize}
    \item Co-led the creation of the first Youreka national financial aid and equity, diversity, and inclusion (EDI) policies; funded all 12 students who applied for bursaries for the 2021-22 program
    \item Spearheaded the first professional development and pedagogy training for 17 undergraduate teachers across Canada
\end{itemize} \vspace{1em}
\textit{Vice President of Academics (May 2019 -- Jun. 2021)}
\begin{itemize}
    \item Taught a ten-week science program to a cohort of 30 high school and undergraduate students in Edmonton
    \item Taught all Youreka Canada branches and created slide sets, worksheets, and Python 3 code during the COVID-19 pandemic
    \item Spearheaded a pilot project for Youreka Edmonton that doubled student enrollment from 30 to 60 students from 2019 to 2020
\end{itemize} \vspace{1em}
% \textit{Undergraduate Research Lead (Feb. 2019 -- May 2019)}
% \begin{itemize}
%     \item Mentored a team of 4 high school students for 4 months about bioinformatics research
%     \item Nominated by my team for the ``Best Undergraduate Research Lead'' award
% \end{itemize} \vspace{1em}

\textbf{Engineering Physics Club at the University of Alberta} \hfill Sep. 2021 -- Jun. 2022 \\
\textit{Vice President External \& Year Representative}
\begin{itemize}
    \item Invited by University of Alberta faculty to align the Engineering Physics curriculum with industry and research needs; engaged multiple stakeholder groups; implemented 2 core classes and 2 electives; preserved the co-op program
    \item Founded and wrote the \href{https://atom-winter-2022.netlify.app/}{Atom Magazine for Engineering Physics}; the first issue attracted 300+ readers in 6 countries
\end{itemize} \vspace{1em}

\textbf{Canadian Blood Services} \hfill Jun. 2018 -- Jan. 2021 \\
\textit{NextGen Lifeline Committee Executive}
\begin{itemize}
    \item Coordinated and organized blood donation and stem cell events (e.g., patient campaigns) with staff and volunteers
    \item Created a software management system for volunteer contracts and event data
    \item Personally recruited 130+ blood donors and 350+ stem cell donors
\end{itemize}


% ================================== TECHNICAL SKILLS ================================== 
\section*{\textcolor{my_colour}{Skills and Hobbies}}
\vspace{-.25em} \hrulefill \vspace{.25em}

\textbf{Certifications} \hfill \parbox[t]{.8\linewidth}{Standard First Aid CPR and AED Level C, Basic Life Support, DELF B1, Class 5 Driver's Licence}

\textbf{Skills} \hfill \parbox[t]{.8\linewidth}{Machine learning, reinforcement learning, data science, research, teaching, curriculum development}

\textbf{Programming} \hfill \parbox[t]{.8\linewidth}{R, Python, C++, MATLAB, VHDL}

\textbf{Software} \hfill \parbox[t]{0.8\linewidth}{Simulink, FMRIB Software Library, Git, \LaTeX, HTML, CSS, R Markdown, Microsoft Office}

\textbf{Electronics} \hfill \parbox[t]{0.8\linewidth}{Arduino, Raspberry Pi, Zybo Z7 FPGA, oscilloscope, digital multimeter, Exo-H3}

\textbf{Hobbies and Interests} \hfill \parbox[t]{.8\linewidth}{Fencing, running, rowing, skiing, reading, programming, math}

\end{document}
